---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
load the essiential packages
```{r}
library(ggplot2)
library(data.table)
```
read data from my work directary
```{r}
df <- read.csv("activity.csv",stringsAsFactors=FALSE)
dt <- data.table(df)
```
process the data 
```{r}
dt$date <- as.Date(dt$date)
setkey(dt, date, interval)
```

## What is mean total number of steps taken per day?
Congrugate the steps by day
```{r}
steps_day <- dt[, list(totalsteps = sum(steps)), date]
```
Plot "total number of steps taken each day"
```{r}
ggplot(steps_day,aes(x=totalsteps)) + geom_histogram() +  
xlab("Total number of steps") +
ggtitle("total number of steps taken each day")+ theme_bw()
```
Calculate the mean and median total number of steps taken per day
```{r}
median(steps_day$totalsteps,na.rm = TRUE)
mean(steps_day$totalsteps,na.rm = TRUE)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
